### 2022-04-19 GB_Simulation_3Species.Rmd
s

#NEW VERSION that has week breaks for entire simulation and allows fishing on just 1 day per week
source("R/init_sim_Bens_nofish.R")
sim <- init_sim_Bens_nofish(nrows = nrow(hab$hab$spp1), ncols = ncol(hab$hab$spp1), n_years = 5, n_tows_day = 1,n_days_wk_fished = 1, n_fleets = 1, n_vessels = 1, n_species = 3,
                            move_freq = 1)

>>>>

#NEW VERSION that has week breaks for entire simulation and allows fishing on just 1 day per week
source("R/init_sim_Bens_nofish.R")
sim <- init_sim_Bens_nofish(nrows = nrow(hab$hab$spp1), ncols = ncol(hab$hab$spp1), n_years = 22, n_tows_day = 1,n_days_wk_fished = 1, n_fleets = 1, n_vessels = 1, n_species = 3,
                            move_freq = 1)
